### 2012-05-26 GUIErrorDetector/paper/introduction.tex
change the quotation

\makeatletter
\newenvironment{myquotation}
               {\list{}{\listparindent=0pt%whatever you need
                        \itemindent    \listparindent
                        \leftmargin=14pt%  whatever you need
                        \rightmargin=14pt%whatever you need
                        \topsep=0pt%%%%%  whatever you need
                        \parsep        \z@ \@plus\p@}%
                \item\relax}
               {\endlist}
\makeatother

%\begin{myquotation}
%this is on purpose. if not, the code in the next page will be
%scattered into 2 pages
\vspace{-2mm}
\begin{quotation}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{quotation}
\vspace{-2mm}
%\end{myquotation}

>>>>

\makeatletter
\newenvironment{myquotation}
               {\list{}{\listparindent=0pt%whatever you need
                        \itemindent    \listparindent
                        \leftmargin=10pt%  whatever you need
                        \rightmargin=0pt%whatever you need
                        \topsep=0pt%%%%%  whatever you need
                        \parsep        \z@ \@plus\p@}%
                \item\relax}
               {\endlist}
\makeatother

%\begin{myquotation}
%this is on purpose. if not, the code in the next page will be
%scattered into 2 pages
%\vspace{-2mm}
\begin{myquotation}
All GUI objects, including visual components and data models, must be
 accessed exclusively from the \textit{event dispatching thread}.
\end{myquotation}
%\vspace{-2mm}
%\end{myquotation}
